### 2025-04-15 README.qmd
Updated read_me

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

# article3

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "From Stone to Tool: How Raw Materials Influenced Upper Paleolithic Technology in Southwestern Iberia (Vale Boi)"
```

# from-stone-to-tool

@@

> Belmiro, J., Bicho, N., Terradas, X., Cascalheira, J., (in prep). _`r Title`_. Archaeological and Anthropological Sciences <https://doi.org/xxx/xxx>

@@

> Belmiro, J., Bicho, N., Terradas, X., Cascalheira, J., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/UWMPK>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis.
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
